Why do we Eval?\\[2mm]\Large A large-scale study of Eval usage in R

### 2020-12-16 paper/main.tex

To provide a picture of \eval usage in R, we recorded \Allcalls
invocations of \eval and its variants in the CRAN corpus. These calls
were obtained by XXX runs, with runs that did not trigger \eval
discarded. Out of the \Corpus CRAN packages with \eval call sites, we
observed calls in \Triggeredpkgs packages, the difference can be chalk
down to incomplete code coverage and occasional failures due to our
pipeline.

@@

Figure~\ref{freq} shows the number of \evals generated by each package
over all runs that invoked functions in that package. Out of the XXX
packages in the corpus, XXX call have a low frequency of \eval calls,
with fewer than 100 of them. On the other hand, XXX packages call eval
more than 1,000 times, with one package (???) calling it XXXX times.

>>>>

To provide a picture of \eval usage in R, we recorded \Allcalls
invocations of \eval and its variants in the CRAN corpus. These calls
were obtained by \Nbruns runs, with runs that did not trigger \eval
discarded. Out of the \NbStaticAtLeastOneCallSite CRAN packages(among the \Corpus packages of our corpus) with \eval call sites, we
observed calls in \Triggeredpkgs packages, the difference can be chalk
down to incomplete code coverage and occasional failures due to our
pipeline.

@@

Figure~\ref{freq} shows the number of \evals generated by each package
over all runs that invoked functions in that package. Out of the \Corpus
packages in the corpus, \EvalCallsLessHundred packages have a low frequency of \eval calls,
with fewer than 100 of them. On the other hand, \EvalCallsMoreThousand packages call eval
more than 1,000 times, with one package (\MaxEvalCallPackage) calling it \MaxEvalCallsRnd times.
